---
title: "Visualization Part 1"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)

library(hexbin)
```

Import the weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USW00022534", "USS0023B17S"), # assess data online allowed by rnoaa package
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2021-01-01",
    date_max = "2022-12-31") %>%
  mutate(
    name = case_match(
      id, 
      "USW00094728" ~ "CentralPark_NY", 
      "USW00022534" ~ "Molokai_HI",
      "USS0023B17S" ~ "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
 ## Scatterplots
 
 Create scatterplot
 
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

new approach, same plot

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

save and edit plot object

```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot = geom_point()
```


## Advanced scatterplot

start with the same one

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() + 
  geom_smooth(se = FALSE) # does not show confidence interval band
```

what about 'aes' placement?

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()
```

facet some things

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.2, size = .2) + # alpha level defines transparency
  geom_smooth(se = FALSE, size = .2) +
  facet_grid(. ~ name) # show graph separately by column, according to name of the place.
```


by default, the larger value of variable in 'alpha = variable', the lower the transparency. To reverse this, use 'scale_alpha(trans = "reverse")' for ***continuous variable*** and scale_alpha_discrete(reverse = TRUE) for ***discrete variable***.

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name, alpha = tmin)) +
  geom_point() + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name) +
  scale_alpha(trans = "reverse")
```


combine elements and try new plot

```{r}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(alpha = .5, aes(size = prcp)) + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```


## some small notes

how many geom have to exist

have whatever geoms you want

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```

use a neat geom

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_density2d() +
  geom_point(alpha = .3)
```


## Univeriate plots

